SUPPLEMENTARY INFORMATION: NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-11-22 SI.tex
Updates from Overleaf

\section{Databank content}

\begin{figure}
  \includegraphics[width=\textwidth]{Figures/DataBankChart.pdf}
  \caption{Structure of the NMRlipids databank. Manually added input data (blue boxes) includes basic information on the simulation, permanent links to the raw data, and experimental data if available. The databank entries (red box) and analysis results (green boxes), locating at \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations} are automatically generated by the computer programs included in the NMRlipids databank (yellow boxes). Because raw data are not permanently stored but can be accessed based on the information in the databank, this connection is marked with the dashed line. }\label{DatabankStructure}
\end{figure}

\begin{table}[]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (e.g. Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI & \\
    TPR & Name of the topology file found from DOI (trp file in the case of Gromacs) & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. \tablefootnote{For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100.} & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. \tablefootnote{For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100.} \\
    COMPOSITION & Molecules names used in the simulation and corresponding mapping files (see section \ref{naming}) & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations, empty for all atom simulations & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data. & User given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data. & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication, etc. & \\
    FF\_DATE &  Date when force field parameters were accessed on the gives source (day/month/year). & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD. & \\
    CPT & Name of the Gromacs checkpoint file. & \\
    LOG & Name of the Gromacs log file. & \\
    TOP & Name of the Gromacs top file. & \\
    GRO & Name of the Gromacs gro file. & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data. \\
    TRJLENGTH & Lenght of the trajectory (ps). & \\
    TEMPERATURE & Temperature of the simulation. & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation. & \\
    DATEOFRUNNIG & Date when added into the databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
    Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file. & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{c|c}
        Abbreviation & Molecule name \\
        \hline
        POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine\\
        POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
        POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
        POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
        CHOL & cholesterol \\
        DHMDMAB & dihexadecyldimethylammonium \\
        \hline
        POT & potassium ion \\
        SOD & sodium ion \\
        CLA & chloride ion \\
        CAL & calcium ion \\
        SOL & water \\
    \end{tabular}
    \caption{Abbreviations used in the databank}
    \label{tab:abbreviations}
\end{table}

@@

>>>>

%\newpage
\pagebreak
\section{Databank content}

\begin{figure}[!h]
  \includegraphics[width=\textwidth]{Figures/DataBankChart.pdf}
  \caption{Structure of the NMRlipids databank. Manually added input data (blue boxes) includes basic information on the simulation, permanent links to the raw data, and experimental data if available. The databank entries (red box) and analysis results (green boxes), locating at \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations} are automatically generated by the computer programs included in the NMRlipids databank (yellow boxes). Because raw data are not permanently stored but can be accessed based on the information in the databank, this connection is marked with the dashed line.}
  \label{DatabankStructure}
\end{figure}

\begin{table}[]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (e.g. Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI (trr or xtc for Gromacs, dcd for OpenMM) & \\
    TPR (Gromacs) & Name of the tpr topology file found from DOI for Gromacs simulations & \\
    PDB (OpenMM) & Name of the pdb file found from DOI for OpenMM simulations & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. 
    %For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100. 
    & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. 
    %For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100. 
    & \\
    COMPOSITION & Dictionary connecting universal molecule and atom names to the ones used in simulation & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations using buildH program~\cite{santuz21}. Empty for all atom simulations. & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data. & User given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data. & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication, etc. & \\
    FF\_DATE &  Date when force field parameters were accessed on the gives source (day/month/year). & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD. & \\
    CPT & Name of the Gromacs checkpoint file. & \\
    LOG & Name of the Gromacs log file. & \\
    GRO & Name of the Gromacs gro file. & \\
    TOP & Name of top file for Gromacs or psf file for OpenMM. & \\
    CRD & Name of crd file for OpenMM. & \\
    WARNINGS & Dictionary containing information about unusual features in the trajectory, such as ambiguous atom names, membrane normal not oriented in z-direction, old Gromacs version used, etc. & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data. \\
    TRJLENGTH & Lenght of the trajectory (ps). & \\
    TEMPERATURE & Temperature of the simulation. & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation. & \\
    DATEOFRUNNIG & Date when added into the databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules in both leaflets and numbers of other molecules are added to the dictionary. & \\
    ID & Unique ID number to ease the analyses. & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

%\begin{table}[h]
%    \centering
%    \begin{tabular}{c|c}
%        Abbreviation & Molecule name \\
%        \hline
%        POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine\\
%        POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
%        POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
%        POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
%        CHOL & cholesterol \\
%        DHMDMAB & dihexadecyldimethylammonium \\
%        \hline
%        POT & potassium ion \\
%%        SOD & sodium ion \\
 %       CLA & chloride ion \\
%        CAL & calcium ion \\
%%    \end{tabular}
 %   \caption{Abbreviations used in the databank}
%    \label{tab:abbreviations}
%\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{c&c}
        Abbreviation & Molecule name \\
        \hline
POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine  \\
POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
PYPC & 1-(16:0)-2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
PAzePCprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine protonated \\
PAzePCdeprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine deprotonated \\
DMPC & 1,2-dimyristoyl-sn-glycero-3-phosphocholine \\
DPPC & 1,2-dipalmitoyl-sn-glycero-3-phosphocholine \\
DPPE & 1,2-dipalmitoyl-sn-glycero-3-phosphoethanolamine \\
DPPG & 1,2-dipalmitoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) \\
DEPC & 1,2-dierucoyl-sn-glycero-3-phosphocholine \\
DRPC & 1,2-(14:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
DYPC & 1,2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
DLPC & 1,2-dilauroyl-sn-glycero-3-phosphocholine \\
DLIPC& 1,2-dilinoleoyl-sn-glycero-3-phosphocholine \\
DOG  & 1,2-dioleoyl-sn-glycerol \\
DOPC & 1,2-dioleoyl-sn-glycero-3-phosphocholine \\
DOPE & 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine \\
DDOPC& 1,2-didocosahexaenoyl-sn-glycero-3-phosphocholine \\
DOPS & 1,2-dioleoyl-sn-glycero-3-phospho-L-serine \\
DSPC & 1,2-distearoyl-sn-glycero-3-phosphocholine \\
DAPC & 1,2-diarachidonoyl-sn-glycero-3-phosphocholine \\
SLiPC & 1-(18:0)-2-(18:2 $^{\Delta9,12}$)-sn-glycero-3-phosphocholine  \\
DMTAP & 1,2-dimyristoyl-3-trimethylammonium-propane \\
SOPC & 1-stearoyl-2-oleoyl-sn-glycero-3-phosphocholine \\
POPI & \\ 
SAPI & \\
SLPI &  \\
SDG & 1-stearoyl-2-docosahexaenoyl-sn-glycerol \\
SDPE & 1-stearoyl-2-docosahexaenoyl-sn-glycero-3-phosphoethanolamine \\
CER  & N-palmitoyl-D-erythro-sphingosine \\
CHOL & cholesterol  \\
DCHOL & 18,19-di-nor-cholesterol \\
DHMDMAB & dihexadecyldimethylammonium  \\
\hline
POT & potassium ion  \\
SOD & sodium ion  \\
CLA & chloride ion \\
CAL & calcium ion  \\
CES & caesium ion \\
SOL & water  \\
    \end{tabular}
    \caption{Abbreviations for molecules used in the databank}
    \label{tab:abbreviations}
\end{table}

@@

\pagebreak
\section{Experimental data}
\subsection{NMR experiments}
Acyl chain order parameters of POPE and POPG were analyzed from the experiments that were used to determine headgroup order parameters in Ref.~\citenum{bacle21}.

\subsection{X-ray scattering experiments}
X-ray scattering form factors contributed to the NMRlipids III project are included in the databank (\url{http://nmrlipids.blogspot.com/2022/09/nmrlipids-iii-including-lipid-lateral.html}).
